\tool: Revisiting BadUSB with Type-C

### 2021-03-12 WOOT/Files/experiment.tex
remove nonsense

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are 94,058 entries of data from 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expressions are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts could be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

In the manual analysis, we replayed the videos and extracted sensitive information.
Accounts of internet applications such as Apple, iCloud, Facebook, Twitter can be obtained.
Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboards of the financial applications, can be clearly recorded.
We can obtain the plain text of passwords such as WiFi passwords.
Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

>>>>

After collecting the captured videos of the mobile phone, we analyzed the videos automatically.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are 94,058 entries of data from 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expressions are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts could be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.
